---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bmicalc

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/wf-id/bmicalc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/wf-id/bmicalc?branch=main)
[![R-CMD-check](https://github.com/wf-id/bmicalc/workflows/R-CMD-check/badge.svg)](https://github.com/wf-id/bmicalc/actions)
<!-- badges: end -->

The goal of bmicalc is to facilitate the rapid assignment of growth percentiles by key demographics.
Currently only weight is implemented.

## Installation

You can install the development version of bmicalc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wf-id/bmicalc")
```

## Example

This is a basic example which shows you how to calculate the weight percentile for an individual:

```{r example}
library(bmicalc)

generate_weight_percentile(sex = "Female", age = 2, weight = 12)
```

If you are at the extremes, you will get a warning message:

```{r}
generate_weight_percentile(sex = "Female", age = 2, weight = 2000)
```

```{r}
generate_weight_percentile(sex = "Female", age = 2, weight = 0.1)
```
